The pollination trade-off

### 2018-12-09 paper/manuscript.Rmd
Fix word count in front matter

**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters, approx. `r format(round(msc_wordcount$n_words_stri/10)*10-340, big.mark = ",")` words (includes draft info, excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` reading time.

>>>>

**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters, approx. `r format(round(msc_wordcount$n_words_stri/10)*10, big.mark = ",")` words (excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` min. reading time.
